Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Add specific comments on which power contributions are accounted for.

As previuosly explained, we performed numerical simulations using a previously developed AMR model, varying the profile-specific and geometric parameters. We also implemented a model to calculate the power consumption of a novel fluid management system, which is a topic not yet extensively studied in the literature. The output variables from this integrated model are the cooling capacity, the several power contributions (\colorbox{yellow}{specify}) and the coefficient of performance (COP).

>>>>

As previuosly explained, we performed numerical simulations using a previously developed AMR model, varying the profile-specific and geometric parameters. We also implemented a model to calculate the power consumption of a novel fluid management system, which is a topic not yet extensively studied in the literature. The output variables from this integrated model are the cooling capacity, the several power contributions (the magnetic power to magnetize the material, the pumping power to overcome pressure drop in the regenerator, and the power to actuate the electronic valves) and the coefficient of performance (COP).
